\title{Image Processing and Analysis Course I\\
Basics}
\author{Kota Miura\\
\\
  Centre for Molecular and Cellular Imaging,\\
  EMBL Heidelberg,\\
  Germany\\
\\
\texttt{miura@embl.de}
}

\date{\today}

%\maketitle
\pagestyle{empty}
\titleTH
\clearpage
\pagestyle{fancyplain}
\begin{abstract}
\HRule

\textbf{Aim: students acquire basic knowledge and techniques for handling
digital image data by interactively using ImageJ.} \\
\\

NOTE: this textbook was written using the Fiji distribution of ImageJ (IJ ver 1.47n, JRE 1.6.0\_45).
Exercises are recommended to be done using Fiji since most of plugins used in
exercises are pre-installed in Fiji.

Many texts, images and exercises especially for chapter 1.3 and 1.4 were
converted from the textbook of Matlab Image Processing Course in MBL, Woods Hall
(which are originally from a book \textit{Digital Image Processing
using Matlab}, Gonzalez et al, Prentice Hall). I thank Ivan Yudushkin for
providing me with the manual he used there.
Deconvolution tutorial was written by Alessandra Griffa and appears in this
textbook with her kind acceptance to do so.
Figures on stack editing are drawn by S\'{e}bastien Toshi and Julien Colombelli for their course and appear in this textbook for his kind offer. I am pretty much thankful to his figure and am impressed with the way he summarized all the commands related to this.
S\'{e}bastien Toshi also reviewed the article in detail and made may suggestions to improve the text. I thank him a lot for his effort. 


This text is progressively edited. Please ask me when you want to distribute. \\
\\
Compiled on: \today \\
Copyright 2006 - 2016, Kota Miura (http://cmci.embl.de)

\HRule
\end{abstract}
